%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

\cventry
    {Data Scientist} % Job title
    {Eratos} % Organization
    {Melbourne, Australia} % Location
    {Apr. 2024 - } % Date(s)
    {
      \begin{cvitems}
        \item Productionalised scientific climate models for agriculture and climate research for use on Eratos' data platform.
        \item Developed an automatic email system to provide high resolution weather data daily to specific locations.
        \item Maintained a variety of Python client libraries, including writing tests and updating CI/CD pipelines with Github Actions.
      \end{cvitems}
    }

\cventry
    {Technology Intern} % Job title
    {ANZ Banking Group} % Organization
    {Melbourne, Australia} % Location
    {Nov. 2023 - Apr. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Interned under Institutional Banking technology division, across two portfolios.
        \item Developed automation scripts in Python for internal workforce financial planning.
        \item Worked on an extensive machine learning project with institutional credit lending team applying NLP techniques, primarily LLMs, for information retrieval.
      \end{cvitems}
    }

\cventry
    {Research Assistant} % Job title
    {University of Melbourne} % Organization
    {Melbourne, Australia} % Location
    {Mar. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Undertook an applied natural language processing project, experimenting with models for a novel regression task.
        \item Used open source frameworks such as PyTorch extensively.
      \end{cvitems}
    }

\cventry
    {Data Scientist} % Job title
    {Dysrupt Labs} % Organization
    {Melbourne, Australia} % Location
    {Jan. 2023 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed and evaluated inference methods for prediction market data using R and Python.
        \item Created a process for an automated summary report of the platform's data for stakeholders, alongside an accompanying dashboard.
      \end{cvitems}
    }

\cventry
    {Research Intern} % Job title
    {University of Melbourne \& Eratos} % Organization
    {Melbourne, Australia} % Location
    {Nov. 2022 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked together with Eratos, a DataOps company to research user needs and develop tools using climate data in Python.
        \item Conducted user interviews to gather research data and validate product designs.
        \item Prototyped a statistical model for forecasting of bad weather days in the construction industry.
      \end{cvitems}
    }

\cventry
    {Junior Data Analyst} % Job title
    {Revium} % Organization
    {Melbourne, Australia} % Location
    {Nov. 2021 - Oct. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Used Google Marketing Platform (Analytics, Data Studio, Tag Manager) extensively to provide valuable insights for clients.
        \item Created bespoke data visualisations in R and Python, together with dashboards in Power BI.
        \item Built modules for data extraction using APIs from ad and analytics platforms, reducing costs from usage of vendor software.
      \end{cvitems}
    }


%---------------------------------------------------------


  % \cventry
  %   {Private Tutor} % Job title
  %   {Self-Employed} % Organization
  %   {Melbourne, Australia} % Location
  %   {Jan. 2020 - Jan. 2021} % Date(s)
  %   {}

%---------------------------------------------------------
\end{cventries}
